The Practical Application of Computerised Multistage Tests

### 2021-03-02 article.Rmd
Added constraints section

>>>>

## Constraints and Assumptions

This article focuses on practical solutions to problems that may be encountered during a test design. Lack of sufficient data, particularly in the early stages of design, is a perennial problem. The ability to validate the design at an early stage with simulated data is therefore important and will be covered here.

In addition the test delivery system may be restricted in its ability to access the item bank to derive item difficulties. In this case, mapping functions to derive ability estimates and scale scores as well as provision of the cut scores for module routing must be provided in advance of test administration for each panel. We demonstrate methods that can be used to provide these values.
